---
title: "Text-Network Analysis of White & Black Soldiers"
weight: 1
output:
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
---

```{css, echo=FALSE}
/* this chunnk of code centers all of the headings */
h1, h2, h3, h4 {
  text-align: center;
}
```

#### Overview  

In this document, we outline our workflow for "Using Text Networks to Examine American Soldier’s Perspectives on Racial Segregation during World War II." Below, we document how we: 

- Ingest and clean the American Soldier data 
- Create the black soldier response text network 
- Create the white soldier response text network 
- Create the black + white soldier response text network 

#### Data Ingestition 

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
rm(list = ls()) 

# set format for rmd 
knitr::opts_chunk$set(echo = F, fig.width = 8, fig.height = 6)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) ;

# load libraries
library(tidyverse)
library(ggplot2)
library(tidytext)
library(SnowballC)
library(widyr)
library(data.table)
library(stringi)
library(igraph)
library(ggraph)
library(tidygraph)
library(rgexf)

# load data 
data(stop_words)
collapse <- fread("/sfs/qumulo/qhome/kb7hp/git/american-soldier-crdh/data/dictionaries/collapse_words.csv", sep = ",")
#so that stringr doesn't pick up on instances where it is part of another word
collapse <- mutate(collapse, original = paste("\\b", original,"\\b", sep = "")) 
#replace with collapsed words
source(here::here("functions", "load_data.R"))
data$long <- stri_replace_all_regex(data$long, collapse$original, 
                                    collapse$collapse_union, vectorize_all = FALSE)
data$outfits_comment <- stri_replace_all_regex(data$outfits_comment, collapse$original, 
                                               collapse$collapse_union, vectorize_all = FALSE)

# split data by racial group 
S32N <- filter(data, racial_group == "black")
S32W <- filter(data, racial_group == "white")

#Written response to "should soldiers be in separate outfits?"
text77_df <- tibble(row = 1:nrow(S32W), text = S32W$outfits_comment, outfits = S32W$outfits) 
#Written response on overall thoughts on the survey
text78_df <- tibble(row = 1:nrow(S32W), text = S32W$long) 
textn_df <- tibble(row = 1:nrow(S32N), text = S32N$long)
textn_df
```

#### Black soldier response network 

```{r, echo = FALSE, message=FALSE, warning=FALSE}

# this takes the long response for BLACK soldiers and tokenizes the df 
row_n_words <- textn_df %>%
  mutate(section = row_number()) %>%
  filter(section > 0) %>%
  mutate(text = ifelse(str_detect(text, "u.s."), "usa", text)) %>%
  mutate(text = ifelse(str_detect(text, "don‚äôt"), "don't", text)) %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word) %>%
  mutate(word= textstem::lemmatize_words(word)) %>%
  mutate(word= wordStem(word))

# cleans all of the stemming to make the visuals more interpretable 
source(here::here("functions", "unstem_words.R"))
row_n_words <- unstem_words(row_n_words)

# count words co-occuring within sections
word_pairs_n <- row_n_words %>%
  pairwise_count(word, section, sort = TRUE)

# filters the words not freq used 
word_cors_n <- row_n_words %>%
  group_by(word) %>%
  filter(n() >= 20) %>%
  pairwise_cor(word, section, sort = TRUE) %>%
  filter(correlation > .1)

# de-duplicates the edgelist
remove_dups <- igraph::simplify(graph.data.frame(word_cors_n, directed = FALSE), 
                              edge.attr.comb = igraph_opt("edge.attr.comb"),
                              remove.loops = FALSE)
remove_dups <- data.frame(as_edgelist(remove_dups, names = TRUE))

corr_edgelist <- remove_dups %>% 
  rename(item1 = X1, item2 = X2) %>% 
  left_join(word_cors_n, by = c("item1", "item2")) %>% 
  arrange(-correlation)

# removes the numbers 
number_list <- c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15")
corr_edgelist_n <- corr_edgelist %>% 
  rename(source = item1, target = item2, weight = correlation) %>%  
  filter(!(source %in% number_list) & !(target %in% number_list)) 

# pull out the nodelist 
text_network <- graph.data.frame(corr_edgelist_n, directed = FALSE)
black_nodelist <- data.frame(id = c(1:(igraph::vcount(text_network))), name = igraph::V(text_network)$name)
black_nodelist <- black_nodelist %>% select(-id) %>% rename(id = name) %>% mutate(label = id)

# community detection (using louvain method)
components <- components(text_network)
louvain <- cluster_louvain(text_network)
fstgrdy <- fastgreedy.community(text_network)
black_nodelist$component <- components$membership
black_nodelist$louvain_comm <- louvain$membership
black_nodelist$fstgrdy_comm <- fstgrdy$membership

# centrality metrics 
black_nodelist$deg_cent <- degree(text_network)
black_nodelist$wtd_deg_cent <- strength(text_network)
black_nodelist$eigen_cent <- eigen_centrality(text_network)$vector
black_nodelist$page_rank <- page_rank(text_network)$vector
black_nodelist$auth_score <- authority.score(text_network)$vector
black_nodelist$hub_score <- hub.score(text_network)$vector
black_nodelist$k_core <- coreness(text_network)

# quick look at the network 
set.seed(2016)
corr_edgelist_n %>%
  filter(weight > .1) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = weight), show.legend = TRUE) +
  geom_node_point(color = "#E57200", size = 2) +
  #geom_node_text(aes(label = name), repel = TRUE) +
  ggtitle("Co-Occurences of Words from Black Soldiers' Long \nResponses at the 10% Threshold") +
  theme_void()

write_csv(black_nodelist, "/sfs/qumulo/qhome/kb7hp/git/american-soldier-crdh/data/outputs/cooc32l_black_nodes.csv")
write_csv(corr_edgelist_n, "/sfs/qumulo/qhome/kb7hp/git/american-soldier-crdh/data/outputs/cooc32l_black_edges.csv")

```

#### White soldier response network 

```{r unions, echo = FALSE, message=FALSE, warning=FALSE}

# this takes the long response for WHITE soldiers and tokenizes the df 
row_n_words <- text78_df %>%
  mutate(section = row_number()) %>%
  filter(section > 0) %>%
  mutate(text = ifelse(str_detect(text, "u.s."), "usa", text)) %>%
  mutate(text = ifelse(str_detect(text, "don‚äôt"), "don't", text)) %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word) %>%
  mutate(word= textstem::lemmatize_words(word)) %>%
  mutate(word= wordStem(word))

# cleans all of the stemming to make the visuals more interpretable 
# cleans all of the stemming to make the visuals more interpretable 
source(here::here("functions", "unstem_words.R"))
row_n_words <- unstem_words(row_n_words)

# count words co-occuring within sections
word_pairs_n <- row_n_words %>%
  pairwise_count(word, section, sort = TRUE)

# filters the words not freq used 
word_cors_n <- row_n_words %>%
  group_by(word) %>%
  filter(n() >= 20) %>%
  pairwise_cor(word, section, sort = TRUE) %>%
  filter(correlation > .1)

# de-duplicates the edgelist
remove_dups <- igraph::simplify(graph.data.frame(word_cors_n, directed = FALSE), 
                              edge.attr.comb = igraph_opt("edge.attr.comb"),
                              remove.loops = FALSE)
remove_dups <- data.frame(as_edgelist(remove_dups, names = TRUE))

corr_edgelist <- remove_dups %>% 
  rename(item1 = X1, item2 = X2) %>% 
  left_join(word_cors_n, by = c("item1", "item2")) %>% 
  arrange(-correlation)

# removes the numbers 
number_list <- c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15")
corr_edgelist_w <- corr_edgelist %>% 
  rename(source = item1, target = item2, weight = correlation) %>%  
  filter(!(source %in% number_list) & !(target %in% number_list)) 

# pull out the nodelist 
text_network <- graph.data.frame(corr_edgelist_w, directed = FALSE)
white_nodelist <- data.frame(id = c(1:(igraph::vcount(text_network))), name = igraph::V(text_network)$name)
white_nodelist <- white_nodelist %>% select(-id) %>% rename(id = name) %>% mutate(label = id)

# community detection (using louvain method)
components <- components(text_network)
louvain <- cluster_louvain(text_network)
fstgrdy <- fastgreedy.community(text_network)
white_nodelist$component <- components$membership
white_nodelist$louvain_comm <- louvain$membership
white_nodelist$fstgrdy_comm <- fstgrdy$membership

# centrality metrics 
white_nodelist$deg_cent <- degree(text_network)
white_nodelist$wtd_deg_cent <- strength(text_network)
white_nodelist$eigen_cent <- eigen_centrality(text_network)$vector
white_nodelist$page_rank <- page_rank(text_network)$vector
white_nodelist$auth_score <- authority.score(text_network)$vector
white_nodelist$hub_score <- hub.score(text_network)$vector
white_nodelist$k_core <- coreness(text_network)

# quick look at the network 
set.seed(2016)
corr_edgelist_w %>%
  filter(weight > .1) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = weight), show.legend = TRUE) +
  geom_node_point(color = "#E57200", size = 2) +
  #geom_node_text(aes(label = name), repel = TRUE) +
  ggtitle("Co-Occurences of Words from White Soldiers' Long \nResponses at the 10% Threshold") +
  theme_void()

write_csv(white_nodelist, "/sfs/qumulo/qhome/kb7hp/git/american-soldier-crdh/data/outputs/cooc32l_white_nodes.csv")
write_csv(corr_edgelist_w, "/sfs/qumulo/qhome/kb7hp/git/american-soldier-crdh/data/outputs/cooc32l_white_edges.csv")

```

#### Black + white soldier response network 

```{r}

# add variable names to the edgelists 
comb_edgelist_n <- corr_edgelist_n %>% 
  mutate(group = "black")
comb_edgelist_w <- corr_edgelist_w %>% 
  mutate(group = "white")

# rbind the edgelists together  
comb_edgelist_wn <- comb_edgelist_n %>% 
  bind_rows(comb_edgelist_w) %>% 
  arrange(-weight)

# quick look at the network 
set.seed(2016)
comb_edgelist_wn %>%
  filter(weight > .1) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = weight, colour = group), show.legend = TRUE) +
  geom_node_point(color = "#000080", size = 2) +
  scale_edge_colour_manual(values=c("black" = "#E57200", "white" = "#628ed8"))+
  ggtitle("Co-Occurences of Words from White and Black Soldiers' Long \nResponses at the 10% Threshold") +
  theme_void()
```

#### Creating the Gephi Visualizations 

- To do this, we need to create reproducible metrics in `igraph` that we output to nodelists in `.csv` and edgelists in `.gexf`. 

```{r}
# pull out the nodelist 
text_network <- graph.data.frame(comb_edgelist_wn, directed = FALSE)
combined_nodelist <- data.frame(id = c(1:(igraph::vcount(text_network))), 
                                name = igraph::V(text_network)$name)
combined_nodelist <- combined_nodelist 

# community detection (using louvain method)
components <- components(text_network)
louvain <- cluster_louvain(text_network)
#fstgrdy <- fastgreedy.community(text_network)
combined_nodelist$component <- components$membership
combined_nodelist$louvain_comm <- louvain$membership
#combined_nodelist$fstgrdy_comm <- fstgrdy$membership

# centrality metrics 
combined_nodelist$deg_cent <- degree(text_network)
combined_nodelist$wtd_deg_cent <- strength(text_network)
combined_nodelist$eigen_cent <- eigen_centrality(text_network)$vector
combined_nodelist$page_rank <- page_rank(text_network)$vector
combined_nodelist$auth_score <- authority.score(text_network)$vector
combined_nodelist$hub_score <- hub.score(text_network)$vector
combined_nodelist$k_core <- coreness(text_network)

# to read the graph into gephi with weighted edges AND edge attributes 
# we have to convert the file into a gexf object like this: 
edgelist_simplified <- as.data.frame(as_edgelist(text_network, names = FALSE)) %>% 
  rename(Source = V1, Target = V2)
edgelist_attributes <- comb_edgelist_wn %>% select(weight, group) %>% 
  rename(Weight = weight, Group = group)
gexf_file <- write.gexf(nodes=combined_nodelist %>% select(id, name), 
                        edges=edgelist_simplified, edgesAtt=edgelist_attributes, 
                        output = "~/git/american-soldier-crdh/data/outputs/cooc32l_wb_network.gexf")

final_nodelist <- combined_nodelist %>% select(-id) %>% rename(id = name) %>% mutate(label = id)

# and then save the edgelist and nodelist 
write_csv(final_nodelist, "/sfs/qumulo/qhome/kb7hp/git/american-soldier-crdh/data/outputs/cooc32l_wb_nodes.csv")
write_csv(comb_edgelist_wn, "/sfs/qumulo/qhome/kb7hp/git/american-soldier-crdh/data/outputs/cooc32l_wb_edges.csv")

```























